---
title: "c3s2datasets README"
output: github_document
---

# c3s2datasets


## Installation

You can install the development version of c3s2datasets from GitHub with:

```r
install.packages("devtools")
devtools::install_github("MACS40700/c3s2datasets")
```

## Available Datasets

The following datasets are available in this package:

| Dataset Name | Description |
|--------------|-------------|
| chicago_311 | Chicago 311 Requests (2019–2021) |
| chicago_community_areas_map | Chicago Community Areas (Current) GeoJSON |
| chicago_crimes | Sample Chicago Crime Data (2017, Source: City of Chicago Crime Data) |
| cook_county_inc_map | Cook County Incorporated Areas GeoJSON |
| illinois_baby_names | Popular Baby Names in Illinois (1910–2023) |
| instructional_staff | Distribution of U.S. Faculty Appointments by Type (1975–2011) |
| scorecard | U.S. Colleges and Universities: Admissions, Costs, and Outcomes |
| superheroes | Comic Book Superheroes and Villains (100 Characters) |
| USCongress | Sample Legislative Bills Dataset |
| us_states_map | US States Shapefile (2020, 1:5M, Census Bureau) |
| yob1880 | Popular Baby Names in the United States (1880) |
| yob2023 | Popular Baby Names in the United States (2023) |

## Examples

```{r}
library(c3s2datasets)
library(skimr)
library(sf)
library(ggplot2)
```

```{r}
instructional_staff
```

```{r}
superheroes
```

```{r}
mainland <- us_states_map[!(us_states_map$NAME %in% c("Alaska", "Hawaii", "Puerto Rico",
                                        "Guam", "American Samoa", 
                                        "Commonwealth of the Northern Mariana Islands", 
                                        "United States Virgin Islands")), ]
ggplot(mainland) +
  geom_sf() +
  coord_sf() +
  theme_minimal()
```

```{r}
ggplot(chicago_community_areas_map) +
  geom_sf() +
  coord_sf() +
  theme_minimal()
```
